Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 SupportingInformation.Rmd
Table S1 made with italic font

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tinytex)
library(tibble)
aphid_info <- tibble(c1=c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
                       "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
                       "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
                       "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
                     c2=c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
                       "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
                       "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
                       "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)
knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = c("Common name", "Latin binomial"))
```

>>>>

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tinytex)
library(tibble)
library(kableExtra)
library(dplyr)
aphid_info <- tibble(c1=c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
                       "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
                       "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
                       "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
                     c2=c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
                       "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
                       "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
                       "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)

knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = c("", ""))%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1),align = "l",line=F)
```
